---
output: github_document
---

# messy

A package that attempts to remedy some of the difficulties of cleaning data composed of survey inputs. Often times when trying to lump or clean up a categorical variable that was a survey input you'll come across things like "The United States", "the united states", or "THE UNITES STATES". It can be time consuming and frustrating to try to identify each capitalization variant and not all of us are `stringr` masters. All that `Messy` does is gives a nice way to automate the process of testing for all capitalization variants in a variable.

The developmental version of the package can be installed through github using

```{r, eval = FALSE}
devtools::install_github("joshyam-k/messy")
```

## How to use the package

I envision the main function in the package, `messy::messy_string` to be used inside of `dplyr::case_when` as follows.

Suppose we have the following data frame:

```{r, warning = FALSE, message = FALSE}
library(tibble)
library(dplyr)
library(messy)

survey <- tibble(
  country = c('The United States', "the United states", "United kingdom", "United Kingdom"),
  age = 24:27
)
```

We'd like to clean up our categorical variable and in this example we could do it by hand, but in a more large scale case it would be nice to use `messy::messy_string`

`messy_string` takes a string as an input and outputs capitalization variants of that string. For example:

```{r}
messy_string("the united states")
```

This can be used directly inside of `case_when` for a much easier cleaning process!

```{r}
survey %>% 
  mutate(
    country_clean = case_when(
      country %in% messy_string("the united states") ~ "USA",
      country %in% messy_string("united kingdom") ~ "UK"
    )
  )
```

